### 2017-09-29 TF-vldb2018/sec-intro.tex

%Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
The {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts such that every team satisfies the skill requirements of a certain task.
Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed for \teamF,
and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
 (a) minimizing team communication costs,
defined with \eg the diameter, minimum spanning tree and the sum of pairwise member distances of the induced subgraph~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}, and
(b) maximizing team communication relations,
\eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting by introducing a lower bound on the number of individuals with a specific skill in a team, and an upper bound of the total team members, respectively.

@@

One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,GajewarS12,realTeamForm13}, can hardly find a desired team.
They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (a)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (b)).
 \end{example}

@@

A natural question is how to further capture the {\em structural and capacity constraints} in a unified model for team formation?
We  introduce a revision of {\em graph pattern matching} for team formation to fill in this gap.
% 
Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.  Essentially, we utilize patterns to captures the structural constraint, and revise the semantics of graph pattern matching for team formation. For instance, a desired team requirement can be specified by the pattern $P_1$ (ignore dashed edges) in Fig.~\ref{fig-motivation-example}, in which nodes represent the skill requirements,  edges specify the topology constraint, and the bounds on nodes are the capacity constraint.

@@

Another issue is that team formation is accompanied with a highly dynamic situation. It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}. Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. We illustrate this with an example.

@@

\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation (Section~\ref{sec-tsim}).
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs .
To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for handling separate and simultaneous pattern and data updates.

>>>>

%Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
The {\em top-$k$ team formation} problem is to find a list of $k$ highly collaborative teams of experts such that every team satisfies the skill requirements of a certain task.
Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed,
and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
 (a) minimizing team communication costs,
defined with \eg the diameter, minimum spanning tree and the sum of pairwise member distances of the induced subgraph~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}, and
(b) maximizing team communication relations,
\eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting by introducing a lower bound on the number of individuals with a specific skill in a team, and an upper bound of the total team members, respectively.

@@

One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,realTeamForm13}, can hardly find a desired team.
They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (a)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (b)).
 \end{example}

@@

A natural question is how to further capture the {\em structural and capacity constraints} in a unified model for team formation?
We  introduce a revision of {\em graph pattern matching} for team formation to fill in this gap.
% 
Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.  Essentially, we utilize patterns to capture the structural constraint, and revise the semantics of graph pattern matching for team formation. For instance, a desired team requirement can be specified by the pattern $P_1$ (ignore dashed edges) in Fig.~\ref{fig-motivation-example}, in which nodes represent the skill requirements,  edges specify the topology constraint, and the bounds on nodes are the capacity constraint.

@@

Another issue is that team formation is accompanied with a highly dynamic environment. It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}. Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. We show this with an example.

@@

\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation (Section~\ref{sec-tsim}).
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs.
To cope with the highly dynamic environment of team formation, we also formulate the dynamic top-$k$ team formation problem  (Section~\ref{sec-tsim}), for handling separate and simultaneous pattern and data updates.

### 2017-09-29 TF-vldb2018/sec-tsim.tex

\sstab(2) Different from strong simulation with balls having a fixed radius (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is flexible, only less than a user specified upper bound.

>>>>

\sstab(2) Different from strong simulation with balls having a fixed radius (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is flexible, and is only less than a user specified upper bound.
